Modeling a declining count variable

### 2021-11-20 text/08/declining-count-model.Rmd
Removed backslashes

---
title: Modeling a declining count variable
author: Steve Simon
date: 2008-06-14
categories:
- Blog post
tags:
- Poisson regression
output: html_document
---
I\'ve been working on an interesting project that requires Poisson
regression. A company sends out a mailing and gets a certain number of
telephone calls back on each of the days following. The number of phone
calls is typically (but not always) highest on the first day afterwards
and declines rapidly on successive days. I wanted to develop a simple
Poisson regression model for this data.

Here\'s an example of this data

@@

For a=8.2 and r=0.58, this equals 19.5. Since we\'ve already seen 19
events, we would expect to see half an event on average for the
remainder the time. You can use the dpois function to estimate
probabilities for a Poisson random variable with a mean of 0.5.

>>>>

---
title: Modeling a declining count variable
author: Steve Simon
date: 2008-06-14
categories:
- Blog post
tags:
- Poisson regression
output: html_document
---
I've been working on an interesting project that requires Poisson
regression. A company sends out a mailing and gets a certain number of
telephone calls back on each of the days following. The number of phone
calls is typically (but not always) highest on the first day afterwards
and declines rapidly on successive days. I wanted to develop a simple
Poisson regression model for this data.

Here's an example of this data

@@

For a=8.2 and r=0.58, this equals 19.5. Since we've already seen 19
events, we would expect to see half an event on average for the
remainder the time. You can use the dpois function to estimate
probabilities for a Poisson random variable with a mean of 0.5.
